A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-14 text/formal-defnition.tex
epsilon -> varepsilon.

\begin{align*}
    % \textrm{Type variables}  &   &                          & X,Y,Z                                                                                                      \\
    % \textrm{Variables}       &   &                          & x,y,z                                                                                                      \\
    % \textrm{Stage variables} &   &                          & \alpha,\beta,\gamma                                                                                        \\
    % \textrm{Stage}           &   &                          & A,B,C                                                                                                      \\
    \textrm{Kinds}           &   & K,J,I,H,G                & ::= * \mid \Pi x:\tau.K                                                                                    \\
    \textrm{Types}           &   & \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau                          \\
%     \textrm{Constants}       &   &                          & c                                                                                                          \\
    \textrm{Terms}           &   & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M                                            \\
                             &   &                          & \ \ \ \ \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M                          \\  
    \textrm{Signature}       &   & \Sigma                   & ::= \emptyset \mid \Sigma, X::K \mid \Sigma, c:\tau                                                                        \\
    \textrm{Contexts}        &   & \Gamma                   & ::= \emptyset \mid  \Gamma,x:\tau @A\ (x\not\in\textrm{Domain}(\G)\ \text{and}\ x\not\in\textrm{FV}(\tau)) \\
\end{align*}

@@

Terms include ordinary (explicitly typed) \(\lambda\)-terms, constants,
whose type is declared in signature $\Sigma$, and the following five forms
related to multi-stage programming:
$\TB_\alpha M$ represents a code fragment; $\TB_\alpha M$ represents escape;
$\Lambda\alpha.M$ is a stage variable abstraction;
$M\ \epsilon$ is an application of $\epsilon$ to a stage variable \AI{I think the usage of ``application'' is wrong again}; and 
$\%_\alpha M$ is an operator for cross-stage persistence.
The prefix operators $\TB_\alpha, \TBL_\alpha$, and $\%_\alpha$ tie stronger than the two forms of applications
and applications are left-associative
and two abstractions extends as far to the right as possible.
For example, $\F\alpha.\lambda x:\I.\TB_\alpha x\ y$ means $\F\alpha.(\lambda x:\I.(\TB_\alpha x)\ y)$.

@@

Next, we define full reduction for \LMD.
Before giving the definition of reduction, we define two kinds of substitutions.
Substitution $M[x\mapsto N]$ is the ordinary capture-avoiding substitution of
$N$ for $x$ in $M$, and we omit its definition here.
Substitution $M[\alpha \mapsto \epsilon]$ of the empty stage
for stage variable $\alpha$ in $M$ is defined below.
\AI{What about $\tau[x \mapsto N], K[x \mapsto N], \tau [\alpha \mapsto \epsilon]$ and $K[\alpha \mapsto \epsilon]$?}

@@

\begin{align*}
	% \newcommand{\SB}{}
	(\lambda x:\tau.M)[\alpha \mapsto \epsilon] & = \lambda x:(\tau[\alpha \mapsto \epsilon]).(M[\alpha \mapsto \epsilon])                                  \\
	(M\ N)[\alpha \mapsto \epsilon]             & = (M[\alpha \mapsto \epsilon])\ (N[\alpha \mapsto \epsilon])                                          \\
	(M\ \epsilon)[\alpha \mapsto \epsilon]      & = (M[\alpha \mapsto \epsilon])\ \epsilon                                                                \\
	(\TB_\alpha M)[\alpha \mapsto \epsilon]      & = M[\alpha \mapsto \epsilon]                                                                          \\
	(\TB_\beta M)[\alpha \mapsto \epsilon]      & = \TB_\beta (M[\alpha \mapsto \epsilon])                               & (\text{if } \alpha \neq \beta) \\
	(\TBL_\alpha M)[\alpha \mapsto \epsilon]     & =  M[\alpha \mapsto \epsilon]                                        &                               \\
	(\TBL_\beta M)[\alpha \mapsto \epsilon]     & = \TBL_\beta (M[\alpha \mapsto \epsilon])                              & (\text{if } \alpha \neq \beta) \\
	(\Lambda\beta.M)[\alpha \mapsto \epsilon]   & = \Lambda\beta.(M[\alpha \mapsto \epsilon])                            & (\text{if } \alpha \neq \beta) \\
	% (\Lambda\beta.M)[\alpha \mapsto \epsilon]   & = \Lambda\beta.M                                                     & (\text{if } \alpha = \beta)    \\
	(\%_\alpha M)[\alpha \mapsto \epsilon]       & = M[\alpha \mapsto \epsilon]                                         &                                  \\
	(\%_\beta M)[\alpha \mapsto \epsilon]       & = \%_{\beta[\alpha \mapsto \epsilon]}(M[\alpha \mapsto \epsilon])      & (\text{if } \alpha \neq \beta) \\
\end{align*}

\begin{definition}[Reduction]
  \AI{It's not clear what are defined here.  You are talking only about rules.
    Something like ``The relations $M \longrightarrow_\beta N$, ... are the least compatible relations closed under the rules below.''}
	There are three reduction rules ($\longrightarrow_\beta, \longrightarrow_\blacklozenge, \longrightarrow_\Lambda$) in \LMD.
	Congruence rules which are omitted from the definition.
	\begin{align*}
		 & (\lambda x:\tau.M) N \longrightarrow_\beta M[x \mapsto N]                       \\
		% & (\Pi x:\tau.\sigma) M \longrightarrow_\gamma \sigma[x \mapsto M] \\
		 & \TBL_\alpha \TB_\alpha M \longrightarrow_\blacklozenge M                        \\
		 & (\Lambda \alpha.M)\ \epsilon \longrightarrow_\Lambda M[\alpha \mapsto \epsilon]
	\end{align*}
	We write $ M \longrightarrow M'$ iff $ M \longrightarrow_\beta M'$, $ M \longrightarrow_\blacklozenge M'$, or $ M \longrightarrow_\Lambda M'$.
\end{definition}

The relation $\longrightarrow_\beta$ represents ordinary $\beta-$reduction in the \(\lambda\)-calculus; the relation 
$\longrightarrow_\blacklozenge$ represents that quotation $\TB_\alpha M$ is canceled by escape and $M$ is spliced into the code fragment surrounding the escape;
the relation $\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\epsilon$ reduces to the body of abstraction
where $\epsilon$ is substituted for the stage variable.
Application of a non-$\epsilon$ stage to a stage abstraction is prohibited in order to simplify \LMD. \AI{This should have been mentioned earlier in the comparison with Hanada--Igarashi.}
There is no reduction rule for CSP as with Hanada and Igarashi \cite{Hanada2014}.
The CSP operator $\%_\alpha$ disappears when $\epsilon$ is substituted to $\alpha$.
% $\TB_\alpha$ and $\TBL_\alpha$ disappears in the same way as $\%_\alpha$.

@@

% Typing rules for a multi-stage calculus
\AI{This paragraph is not very informaticve.  We shouldn't just refer redears to previous work.}
The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp{} are rules for a multi-stage calculus.
They are corresponding to brackets, escape, making a stage abstraction, 
application of $\epsilon$ stage to a stage abstraction, and cross-stage persistence, respectively.
Please check Hanada and Igarashi \cite{Hanada2014} and Tsukada and Igarashi \cite{Tsukada} for details of these rules.

\begin{figure}
	\begin{center}
		\infrule[\TConst]{c:\tau \in \Sigma \andalso \G\V \tau::*@A}{\G \V c:\tau @A} \\[2mm]
		\infrule[\TVar]{x:\tau @A \in \G \andalso \G\V \tau::*@A}{\G \V x:\tau @A} \\[2mm]
		\infrule[\TAbs]{\G\V \sigma::*@A\andalso\G,x:\sigma@A\V M:\tau @A}{\G\V(\lambda (x:\sigma).M):(\Pi (x:\sigma).\tau)@A} \\[2mm]
		\infrule[\TApp]{\G\V M:(\Pi (x:\sigma).\tau)@A \andalso \G\V N:\sigma@A}{\G\V M\ N : \tau[x\mapsto N]@A} \\[2mm]
		\infrule[\TConv]{\G\V M:\tau @A \andalso \G\V \tau\equiv \sigma :: K@A}{\G\V M:\sigma@A} \\[2mm]
		\infrule[\TTB]{\G\V M:\tau @{A\alpha}}{\G\V\TB_{\alpha}M:\TW_{\alpha}\tau @A} \andalso
		\infrule[\TTBL]{\G\V M:\TW_{\alpha}\tau @A}{\G\V\TBL_{\alpha}M:\tau @{A\alpha}} \\[2mm]
		\infrule[\TGen]{\G\V M:\tau @A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V\Lambda\alpha.M:\forall\alpha.\tau @A} \\[2mm]
		\infrule[\TIns]{\G\V M:\forall\alpha.\tau @A}{\G\V M\ \epsilon:\tau[\alpha \mapsto \epsilon]@A} \andalso
		\infrule[\TCsp]{\G\V M:\tau @A}{\G\V \%_\alpha M:\tau @{A\alpha}}
		\caption{Typing Rules.}
		\label{fig:typing-rules}
	\end{center}
\end{figure}

@@

\begin{figure}
	\begin{center}
		\infrule[\QAbs]{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V M \E N : \rho @A}{\G\V\lambda x:\tau.M \E \lambda x:\sigma.N : (\Pi x:\tau.\rho)@A} \\[2mm]
		\infrule[\QAbs]{\G\V M \E L : (\Pi x:\sigma.\tau)@A \andalso \G\V N \E O : \sigma@A}{\G\V M\ N \E L\ O : \tau[x \mapsto N]@A} \\[2mm]
		\infrule[\QTB]{\G\V M \E N : \tau @{A\alpha}}{\G\V \TB_\alpha M \E \TB_\alpha N : \TW_\alpha \tau @A} \andalso
		\infrule[\QTBL]{\G\V M \E N : \TW_\alpha \tau @A}{\G\V \TBL_\alpha M \E \TBL_\alpha N : \tau @{A\alpha}} \\[2mm]
		\infrule[\QGen]{\G\V M\E N : \tau @A \andalso \alpha \notin \FTV(\G)\cup\FTV(A)}{\G\V \Lambda\alpha.M \E \Lambda\alpha.N : \forall\alpha.\tau @A} \\[2mm]
		\infrule[\QIns]{\G\V M \E N:\forall\alpha.\tau @A}{\G\V M\ \epsilon \E N\ \epsilon : \tau[\alpha \mapsto \epsilon]@A} \andalso
		\infrule[\QCsp]{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau @{A\alpha}} \\[2mm]
		\infrule[\QRefl]{\G\V M:\tau @A}{\G\V M\E M : \tau @A} \andalso
		\infrule[\QSym]{\G\V M\E N : \tau @A}{\G\V N\E M : \tau @A} \\[2mm]
		\infrule[\QTrans]{\G\V M\E N : \tau @A \andalso \G\V N\E L : \tau @A}{\G\V M\E L : \tau @A} \\[2mm]
		\infrule[\QBeta]{\G,x:\sigma@A\V M:\tau @A \andalso \G\V N:\sigma@A}{\G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A} \\[2mm]
		% \infrule{\G\V M:(\Pi x:\sigma.\tau)@A \andalso x\notin \text{FV}(M)}{\G\V(\lambda x:\sigma.M\ x)\E M: (\Pi x:\sigma.\tau)@A}{\QEta} \\[2mm]
		\infrule[\QLambda]{\G\V (\Lambda\alpha.M) : \forall\alpha.\tau @A}{\G\V (\Lambda\alpha.M)\ \epsilon \E M[\alpha \mapsto \epsilon] : \tau[\alpha \mapsto \epsilon]@A} \\[2mm]
		\infrule[\QTBLTB]{\G\V M \E N : \tau @A}{\G\V \TBL_\alpha(\TB_\alpha M) \E N : \tau @A} \hfil
		\infrule[\QPercent]{\G\V M:\tau @{A\alpha} \andalso \G\V M:\tau @A}{\G\V\%_\alpha M \E M : \tau @{A\alpha}}
		\caption{Term Equivalence Rules.}
		\label{fig:term-equivalence-rules}
	\end{center}
\end{figure}

@@

\begin{definition}[Values]
	The family $V^A$ of sets of values, ranged over by $v^A$,
	is defined by following grammar.  In the grammar, $A \neq \epsilon$ is assumed.
	\begin{align*}
		v^\epsilon \in V^\epsilon & ::= \lambda x:\tau.M \mid\ \TB_\alpha v^\alpha \mid \Lambda\alpha.v^\epsilon                                       & \\
		v^A \in V^A               & ::= x \mid \lambda x:\tau.v^A \mid v^A\ v^A \mid\ \TB_\alpha v^{A\alpha} \mid \Lambda\alpha.v^A \mid v^A\ \epsilon & \\
		                         & \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A = A'\alpha \text{ for some } \alpha, A' \neq \epsilon)                          & \\
                                          & \quad\   \mid\ \%_\alpha v^{A'} (\text{if } A = A'\alpha  \text{ for some } \alpha, A')
	\end{align*}
\end{definition}

Values at $\epsilon$ stage are a $\lambda$-abstraction, a quoted code,
or a $\Lambda$ abstraction.  The body of a $\lambda$-abstraction can
be any term but the body of $\Lambda$-abstraction has to a value.  It
means that the body of $\Lambda$-abstraction must be evaluated.  The
side condition for $\TBL_\alpha v^{A'}$ means that escapes in a value
can appear only under nested quotations (because an escape under a
single quotation will splice the code value into the surrounding
code).  See Hanada and Igarashi~\cite{} for details.

\begin{definition}[Evaluation Context and Redex]
  The family of sets $ECtx^A_B$ of evaluation contexts, ranged over by $E^A_B$,
the sets of $\epsilon$-redexes (ranged over by $R^\epsilon$) and $\alpha$-redexes (ranged over by $R^\alpha$) are defined by the following grammar.
	In the grammar, $A$ is assumed to be nonempty (but $B,A'$ can be empty).
	\begin{align*}
		E^\epsilon_B \in ECtx^\epsilon_B & ::= \square\ (\text{if\ } B = \epsilon) \mid E^\epsilon_B\ M \mid v^e\ E^\epsilon_B     
		\mid \TB_\alpha E^\alpha_B \mid \Lambda\alpha.E^\epsilon_B
		\mid E^\epsilon_B\ \epsilon                                                                                                 \\
		E^A_B \in ECtx^A_B               & ::= \square\ (\text{if } A = B) \mid \lambda x:\tau.E^A_B \mid E^A_B\ M \mid v^A\ E^A_B 
		\mid E^\epsilon_B \mid \TB_\alpha E^{A\alpha}_B
		\mid \TBL_\alpha E^{A'}_B \ (\text{where } A'\alpha = A)                                                                    \\
		                                 & \quad \mid \Lambda\alpha.E^\epsilon_B                                                   
		\mid E^A_B\ \epsilon \mid \%_\alpha\ E^{A'}_B \ (\text{where } A'\alpha = A)                                                \\
\\
		 R^\epsilon  & ::= (\lambda x:\tau.M)\ v^\epsilon \mid (\Lambda\alpha.v^\epsilon)\ \epsilon                                       & \\
		 R^\alpha    & ::=\ \TBL_\alpha \TB_\alpha M                                                                                      & \\	\end{align*}
\end{definition}

@@

\begin{definition}[Staged Reduction]
	The staged reduction relation, written $M \longrightarrow_s M'$, is defined by 
	the least relation closed under the rules below.
% \begin{figure}
% 	\begin{center}
		\begin{align*}
			E^A_\epsilon [(\lambda x:\tau.M)\ v^\epsilon]       & \longrightarrow_s E^A_\epsilon[M[x\mapsto v^\epsilon]]             \\
			E^A_\epsilon [(\Lambda\alpha.v^\epsilon)\ \epsilon] & \longrightarrow_s E^A_\epsilon[v^\epsilon[\alpha\mapsto \epsilon]] \\
			E^A_\alpha [\TBL_\alpha \TB_\alpha v^\alpha]        & \longrightarrow_s E^A_\alpha[v^\alpha]                             \\
		\end{align*}
     %    	\caption{Staged Reduction}
     %    	\label{fig:staged-reduction}
     %    \end{center}
     % \end{figure}
\end{definition}

>>>>

\begin{align*}
    % \textrm{Type variables}  &   &                          & X,Y,Z                                                                                                      \\
    % \textrm{Variables}       &   &                          & x,y,z                                                                                                      \\
    % \textrm{Stage variables} &   &                          & \alpha,\beta,\gamma                                                                                        \\
    % \textrm{Stage}           &   &                          & A,B,C                                                                                                      \\
    \textrm{Kinds}           &   & K,J,I,H,G                & ::= * \mid \Pi x:\tau.K                                                                                    \\
    \textrm{Types}           &   & \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} \tau \mid \F\alpha.\tau                          \\
%     \textrm{Constants}       &   &                          & c                                                                                                          \\
    \textrm{Terms}           &   & M,N,L,O,P                & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M                                            \\
                             &   &                          & \ \ \ \ \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \varepsilon \mid \%_\alpha M                          \\  
    \textrm{Signature}       &   & \Sigma                   & ::= \emptyset \mid \Sigma, X::K \mid \Sigma, c:\tau                                                                        \\
    \textrm{Contexts}        &   & \Gamma                   & ::= \emptyset \mid  \Gamma,x:\tau @A\ (x\not\in\textrm{Domain}(\G)\ \text{and}\ x\not\in\textrm{FV}(\tau)) \\
\end{align*}

@@

Terms include ordinary (explicitly typed) \(\lambda\)-terms, constants,
whose type is declared in signature $\Sigma$, and the following five forms
related to multi-stage programming:
$\TB_\alpha M$ represents a code fragment; $\TB_\alpha M$ represents escape;
$\Lambda\alpha.M$ is a stage variable abstraction;
$M\ \varepsilon$ is an application of $\varepsilon$ to a stage variable \AI{I think the usage of ``application'' is wrong again}; and 
$\%_\alpha M$ is an operator for cross-stage persistence.
The prefix operators $\TB_\alpha, \TBL_\alpha$, and $\%_\alpha$ tie stronger than the two forms of applications
and applications are left-associative
and two abstractions extends as far to the right as possible.
For example, $\F\alpha.\lambda x:\I.\TB_\alpha x\ y$ means $\F\alpha.(\lambda x:\I.(\TB_\alpha x)\ y)$.

@@

Next, we define full reduction for \LMD.
Before giving the definition of reduction, we define two kinds of substitutions.
Substitution $M[x\mapsto N]$ is the ordinary capture-avoiding substitution of
$N$ for $x$ in $M$, and we omit its definition here.
Substitution $M[\alpha \mapsto \varepsilon]$ of the empty stage
for stage variable $\alpha$ in $M$ is defined below.
\AI{What about $\tau[x \mapsto N], K[x \mapsto N], \tau [\alpha \mapsto \varepsilon]$ and $K[\alpha \mapsto \varepsilon]$?}

@@

\begin{align*}
	% \newcommand{\SB}{}
	(\lambda x:\tau.M)[\alpha \mapsto \varepsilon] & = \lambda x:(\tau[\alpha \mapsto \varepsilon]).(M[\alpha \mapsto \varepsilon])                                  \\
	(M\ N)[\alpha \mapsto \varepsilon]             & = (M[\alpha \mapsto \varepsilon])\ (N[\alpha \mapsto \varepsilon])                                          \\
	(M\ \varepsilon)[\alpha \mapsto \varepsilon]      & = (M[\alpha \mapsto \varepsilon])\ \varepsilon                                                                \\
	(\TB_\alpha M)[\alpha \mapsto \varepsilon]      & = M[\alpha \mapsto \varepsilon]                                                                          \\
	(\TB_\beta M)[\alpha \mapsto \varepsilon]      & = \TB_\beta (M[\alpha \mapsto \varepsilon])                               & (\text{if } \alpha \neq \beta) \\
	(\TBL_\alpha M)[\alpha \mapsto \varepsilon]     & =  M[\alpha \mapsto \varepsilon]                                        &                               \\
	(\TBL_\beta M)[\alpha \mapsto \varepsilon]     & = \TBL_\beta (M[\alpha \mapsto \varepsilon])                              & (\text{if } \alpha \neq \beta) \\
	(\Lambda\beta.M)[\alpha \mapsto \varepsilon]   & = \Lambda\beta.(M[\alpha \mapsto \varepsilon])                            & (\text{if } \alpha \neq \beta) \\
	% (\Lambda\beta.M)[\alpha \mapsto \varepsilon]   & = \Lambda\beta.M                                                     & (\text{if } \alpha = \beta)    \\
	(\%_\alpha M)[\alpha \mapsto \varepsilon]       & = M[\alpha \mapsto \varepsilon]                                         &                                  \\
	(\%_\beta M)[\alpha \mapsto \varepsilon]       & = \%_{\beta[\alpha \mapsto \varepsilon]}(M[\alpha \mapsto \varepsilon])      & (\text{if } \alpha \neq \beta) \\
\end{align*}

\begin{definition}[Reduction]
  \AI{It's not clear what are defined here.  You are talking only about rules.
    Something like ``The relations $M \longrightarrow_\beta N$, ... are the least compatible relations closed under the rules below.''}
	There are three reduction rules ($\longrightarrow_\beta, \longrightarrow_\blacklozenge, \longrightarrow_\Lambda$) in \LMD.
	Congruence rules which are omitted from the definition.
	\begin{align*}
		 & (\lambda x:\tau.M) N \longrightarrow_\beta M[x \mapsto N]                       \\
		% & (\Pi x:\tau.\sigma) M \longrightarrow_\gamma \sigma[x \mapsto M] \\
		 & \TBL_\alpha \TB_\alpha M \longrightarrow_\blacklozenge M                        \\
		 & (\Lambda \alpha.M)\ \varepsilon \longrightarrow_\Lambda M[\alpha \mapsto \varepsilon]
	\end{align*}
	We write $ M \longrightarrow M'$ iff $ M \longrightarrow_\beta M'$, $ M \longrightarrow_\blacklozenge M'$, or $ M \longrightarrow_\Lambda M'$.
\end{definition}

The relation $\longrightarrow_\beta$ represents ordinary $\beta-$reduction in the \(\lambda\)-calculus; the relation 
$\longrightarrow_\blacklozenge$ represents that quotation $\TB_\alpha M$ is canceled by escape and $M$ is spliced into the code fragment surrounding the escape;
the relation $\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\varepsilon$ reduces to the body of abstraction
where $\varepsilon$ is substituted for the stage variable.
Application of a non-$\varepsilon$ stage to a stage abstraction is prohibited in order to simplify \LMD. \AI{This should have been mentioned earlier in the comparison with Hanada--Igarashi.}
There is no reduction rule for CSP as with Hanada and Igarashi \cite{Hanada2014}.
The CSP operator $\%_\alpha$ disappears when $\varepsilon$ is substituted to $\alpha$.
% $\TB_\alpha$ and $\TBL_\alpha$ disappears in the same way as $\%_\alpha$.

@@

% Typing rules for a multi-stage calculus
\AI{This paragraph is not very informaticve.  We shouldn't just refer redears to previous work.}
The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp{} are rules for a multi-stage calculus.
They are corresponding to brackets, escape, making a stage abstraction, 
application of $\varepsilon$ stage to a stage abstraction, and cross-stage persistence, respectively.
Please check Hanada and Igarashi \cite{Hanada2014} and Tsukada and Igarashi \cite{Tsukada} for details of these rules.

\begin{figure}
	\begin{center}
		\infrule[\TConst]{c:\tau \in \Sigma \andalso \G\V \tau::*@A}{\G \V c:\tau @A} \\[2mm]
		\infrule[\TVar]{x:\tau @A \in \G \andalso \G\V \tau::*@A}{\G \V x:\tau @A} \\[2mm]
		\infrule[\TAbs]{\G\V \sigma::*@A\andalso\G,x:\sigma@A\V M:\tau @A}{\G\V(\lambda (x:\sigma).M):(\Pi (x:\sigma).\tau)@A} \\[2mm]
		\infrule[\TApp]{\G\V M:(\Pi (x:\sigma).\tau)@A \andalso \G\V N:\sigma@A}{\G\V M\ N : \tau[x\mapsto N]@A} \\[2mm]
		\infrule[\TConv]{\G\V M:\tau @A \andalso \G\V \tau\equiv \sigma :: K@A}{\G\V M:\sigma@A} \\[2mm]
		\infrule[\TTB]{\G\V M:\tau @{A\alpha}}{\G\V\TB_{\alpha}M:\TW_{\alpha}\tau @A} \andalso
		\infrule[\TTBL]{\G\V M:\TW_{\alpha}\tau @A}{\G\V\TBL_{\alpha}M:\tau @{A\alpha}} \\[2mm]
		\infrule[\TGen]{\G\V M:\tau @A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V\Lambda\alpha.M:\forall\alpha.\tau @A} \\[2mm]
		\infrule[\TIns]{\G\V M:\forall\alpha.\tau @A}{\G\V M\ \varepsilon:\tau[\alpha \mapsto \varepsilon]@A} \andalso
		\infrule[\TCsp]{\G\V M:\tau @A}{\G\V \%_\alpha M:\tau @{A\alpha}}
		\caption{Typing Rules.}
		\label{fig:typing-rules}
	\end{center}
\end{figure}

@@

\begin{figure}
	\begin{center}
		\infrule[\QAbs]{\G\V \tau \E \sigma :: *@A \andalso \G,x:\tau @A \V M \E N : \rho @A}{\G\V\lambda x:\tau.M \E \lambda x:\sigma.N : (\Pi x:\tau.\rho)@A} \\[2mm]
		\infrule[\QAbs]{\G\V M \E L : (\Pi x:\sigma.\tau)@A \andalso \G\V N \E O : \sigma@A}{\G\V M\ N \E L\ O : \tau[x \mapsto N]@A} \\[2mm]
		\infrule[\QTB]{\G\V M \E N : \tau @{A\alpha}}{\G\V \TB_\alpha M \E \TB_\alpha N : \TW_\alpha \tau @A} \andalso
		\infrule[\QTBL]{\G\V M \E N : \TW_\alpha \tau @A}{\G\V \TBL_\alpha M \E \TBL_\alpha N : \tau @{A\alpha}} \\[2mm]
		\infrule[\QGen]{\G\V M\E N : \tau @A \andalso \alpha \notin \FTV(\G)\cup\FTV(A)}{\G\V \Lambda\alpha.M \E \Lambda\alpha.N : \forall\alpha.\tau @A} \\[2mm]
		\infrule[\QIns]{\G\V M \E N:\forall\alpha.\tau @A}{\G\V M\ \varepsilon \E N\ \varepsilon : \tau[\alpha \mapsto \varepsilon]@A} \andalso
		\infrule[\QCsp]{\G\V M \E N : \tau @A}{\G\V\%_\alpha M \E \%_\alpha N : \tau @{A\alpha}} \\[2mm]
		\infrule[\QRefl]{\G\V M:\tau @A}{\G\V M\E M : \tau @A} \andalso
		\infrule[\QSym]{\G\V M\E N : \tau @A}{\G\V N\E M : \tau @A} \\[2mm]
		\infrule[\QTrans]{\G\V M\E N : \tau @A \andalso \G\V N\E L : \tau @A}{\G\V M\E L : \tau @A} \\[2mm]
		\infrule[\QBeta]{\G,x:\sigma@A\V M:\tau @A \andalso \G\V N:\sigma@A}{\G\V(\lambda x:\sigma.M)\ N\E M[x\mapsto N] : \tau[x \mapsto N]@A} \\[2mm]
		% \infrule{\G\V M:(\Pi x:\sigma.\tau)@A \andalso x\notin \text{FV}(M)}{\G\V(\lambda x:\sigma.M\ x)\E M: (\Pi x:\sigma.\tau)@A}{\QEta} \\[2mm]
		\infrule[\QLambda]{\G\V (\Lambda\alpha.M) : \forall\alpha.\tau @A}{\G\V (\Lambda\alpha.M)\ \varepsilon \E M[\alpha \mapsto \varepsilon] : \tau[\alpha \mapsto \varepsilon]@A} \\[2mm]
		\infrule[\QTBLTB]{\G\V M \E N : \tau @A}{\G\V \TBL_\alpha(\TB_\alpha M) \E N : \tau @A} \hfil
		\infrule[\QPercent]{\G\V M:\tau @{A\alpha} \andalso \G\V M:\tau @A}{\G\V\%_\alpha M \E M : \tau @{A\alpha}}
		\caption{Term Equivalence Rules.}
		\label{fig:term-equivalence-rules}
	\end{center}
\end{figure}

@@

\begin{definition}[Values]
	The family $V^A$ of sets of values, ranged over by $v^A$,
	is defined by following grammar.  In the grammar, $A \neq \varepsilon$ is assumed.
	\begin{align*}
		v^\varepsilon \in V^\varepsilon & ::= \lambda x:\tau.M \mid\ \TB_\alpha v^\alpha \mid \Lambda\alpha.v^\varepsilon                                       & \\
		v^A \in V^A               & ::= x \mid \lambda x:\tau.v^A \mid v^A\ v^A \mid\ \TB_\alpha v^{A\alpha} \mid \Lambda\alpha.v^A \mid v^A\ \varepsilon & \\
		                         & \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A = A'\alpha \text{ for some } \alpha, A' \neq \varepsilon)                          & \\
                                          & \quad\   \mid\ \%_\alpha v^{A'} (\text{if } A = A'\alpha  \text{ for some } \alpha, A')
	\end{align*}
\end{definition}

Values at $\varepsilon$ stage are a $\lambda$-abstraction, a quoted code,
or a $\Lambda$ abstraction.  The body of a $\lambda$-abstraction can
be any term but the body of $\Lambda$-abstraction has to a value.  It
means that the body of $\Lambda$-abstraction must be evaluated.  The
side condition for $\TBL_\alpha v^{A'}$ means that escapes in a value
can appear only under nested quotations (because an escape under a
single quotation will splice the code value into the surrounding
code).  See Hanada and Igarashi~\cite{} for details.

\begin{definition}[Evaluation Context and Redex]
  The family of sets $ECtx^A_B$ of evaluation contexts, ranged over by $E^A_B$,
the sets of $\varepsilon$-redexes (ranged over by $R^\varepsilon$) and $\alpha$-redexes (ranged over by $R^\alpha$) are defined by the following grammar.
	In the grammar, $A$ is assumed to be nonempty (but $B,A'$ can be empty).
	\begin{align*}
		E^\varepsilon_B \in ECtx^\varepsilon_B & ::= \square\ (\text{if\ } B = \varepsilon) \mid E^\varepsilon_B\ M \mid v^e\ E^\varepsilon_B     
		\mid \TB_\alpha E^\alpha_B \mid \Lambda\alpha.E^\varepsilon_B
		\mid E^\varepsilon_B\ \varepsilon                                                                                                 \\
		E^A_B \in ECtx^A_B               & ::= \square\ (\text{if } A = B) \mid \lambda x:\tau.E^A_B \mid E^A_B\ M \mid v^A\ E^A_B 
		\mid E^\varepsilon_B \mid \TB_\alpha E^{A\alpha}_B
		\mid \TBL_\alpha E^{A'}_B \ (\text{where } A'\alpha = A)                                                                    \\
		                                 & \quad \mid \Lambda\alpha.E^\varepsilon_B                                                   
		\mid E^A_B\ \varepsilon \mid \%_\alpha\ E^{A'}_B \ (\text{where } A'\alpha = A)                                                \\
\\
		 R^\varepsilon  & ::= (\lambda x:\tau.M)\ v^\varepsilon \mid (\Lambda\alpha.v^\varepsilon)\ \varepsilon                                       & \\
		 R^\alpha    & ::=\ \TBL_\alpha \TB_\alpha M                                                                                      & \\	\end{align*}
\end{definition}

@@

\begin{definition}[Staged Reduction]
	The staged reduction relation, written $M \longrightarrow_s M'$, is defined by 
	the least relation closed under the rules below.
% \begin{figure}
% 	\begin{center}
		\begin{align*}
			E^A_\varepsilon [(\lambda x:\tau.M)\ v^\varepsilon]       & \longrightarrow_s E^A_\varepsilon[M[x\mapsto v^\varepsilon]]             \\
			E^A_\varepsilon [(\Lambda\alpha.v^\varepsilon)\ \varepsilon] & \longrightarrow_s E^A_\varepsilon[v^\varepsilon[\alpha\mapsto \varepsilon]] \\
			E^A_\alpha [\TBL_\alpha \TB_\alpha v^\alpha]        & \longrightarrow_s E^A_\alpha[v^\alpha]                             \\
		\end{align*}
     %    	\caption{Staged Reduction}
     %    	\label{fig:staged-reduction}
     %    \end{center}
     % \end{figure}
\end{definition}
